Preparing for Potential Closure of European Airspaces due to Reentering Space Objects

### 2025-04-30 paper.qmd
checked Quinten feedback

If we discretaze the area of interest $a$ using H3 cells,
we have

@@

We assume the aircraft impact area to be much larger than the debris
object area so as to neglet the debris impact area.
We can also simplify the geometry of the aircraft and model it as
a rectangular solid with dimesions of wingspan, length and height. 
Now, if the aircraft were stationary, the area exposed to a debris impact would
be the top view, while if the debris were stationary it would be the front view.
In reality the aircraft is moving (manly) horizontally and the debris 
vertically [^balistic_descent], which which allows to express the effective
exposed area, $\varepsilon_k$, as

@@

[^balistic_descent]: *Even for a ballistic coefficient of 50 lbs/ft2, the flight
path angle of a reentering object at 40,000 feet is -86.6 degrees, which
corresponds to nearly vertical descent.
Since most debris objects have ballistic coefficients equal to or 
less than 50 lbs/ft2, the vertical descent assumption is a very
accurate approximation.* [@patera2008]

@@

If we consider historical debris reentry data, we can numerically derive
the debris impact probability as a weighting function by summing up and averaging
all single densities:

@@

Future work will explore the impact of megacostellations and the risk for
European airspace.

# Appendix {.appendix}
# Orbital Elements {#sec-orbitals }

>>>>

If we discretize the area of interest $a$ using H3 cells,
we have

@@

We assume the aircraft impact area to be much larger than the debris
object area so as to neglet the debris impact area.
We can also simplify the geometry of the aircraft and model it as
a rectangular solid with dimesions of wingspan ($W$), length ($L$) and
height ($H$). 
Now, if the aircraft were stationary, the area exposed to a debris impact would
be the top view, while if the debris were stationary it would be the front view.
In reality the aircraft is moving (manly) horizontally and the debris 
vertically [^balistic_descent], which which allows to express the effective
exposed area, $\varepsilon_k$, as

@@

[^balistic_descent]: *Even for a ballistic coefficient of \qty{50}{lbs/ft^2},
the flight path angle of a reentering object at \qty{40000}{ft} is 
\ang{-86.6}, which corresponds to nearly vertical descent.
Since most debris objects have ballistic coefficients equal to or 
less than \qty{50}{lbs/ft^2}, the vertical descent assumption is a very
accurate approximation.* [@patera2008]

@@

If we consider historical uncontrolled debris reentry data, we can numerically
derive the debris impact probability as a weighting function by summing up and
averaging all single densities:

@@

Future work will explore the impact of megacostellations and flight growth
forecast and what would happen in 20, 40, ..., 100 years in varios scenarios
of uncontrolled  reentries and the risk for European airspace.

# Appendix: Orbital Elements {#sec-orbitals }
